---
output: 
  stevetemplates::syllabus:
    latex_engine: xelatex
    dev: cairo_pdf
geometry: margin=1in

title: "CRJU 314: Criminal Law"
author: Ian T. Adams
date: "Fall 2021"

email: "ian.adams@sc.edu"
web: "ianadamsresearch.com"
officehours: "flexible, with notice"
office: "\\shrug"
classroom: "See below"
classhours: "See below"

fontfamily: mathpazo
fontsize: 11pt
header-includes:
   - \linespread{1.05}
---
 <!-- CCCCCCCCnncdxxxxxxx -->
<!-- Fun fact: my cat added this comment as she walked over the keyboard while I was working on this template. -->
<!-- I'm going to keep it going forward. Long live Queen Bea. -->
```{r setup, include=FALSE}
# knitr::opts_chunk$set(cache=FALSE, dev='pdf')
knitr::opts_chunk$set(cache=F,
                      fig.path = 'figs/',
                      cache.path='cache/',
                      warning=F,
                      message=F)

knitr::opts_chunk$set(
                  fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      }
                  )


advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}

options(scipen=999)
library(tidyverse)
library(stevemisc)
#library(ggpmisc)
#library(anonymizer)
# library(ggcal)
#library(stringr)
#library(kfigr)
#library(broom)
library(lubridate)
library(here)
library(kableExtra)


## for grading scheme

grades <- read_csv(here("CRJU 314", "grading-scheme.csv"))

## For discussion grading rubric
rubric <- read_csv(here("CRJU 314", "discussion-rubric.csv"))


# library(RefManageR)
# library(knitcitations)
# library(rcrossref)
#bib <- ReadBib("~/Dropbox/master.bib")
#myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

# Create a calendar for your syllabus ----
# Source: http://svmiller.com/blog/2020/08/a-ggplot-calendar-for-your-semester/

# 1) what is the first Monday of the semester?
# Any number of ways to identify dates in R, but we'll use {lubridate} and the ymd() function here.
# Format: YYYYMMDD. In this example, 4 January 2021.

mon <- ymd(20220815)

# What are some dates you won't be here? In this example, I had a conference on 7 January 2021.
# Spring Break was 15 March 2021 to 19 March 2021.
# ymd(20211125), #for single day
# 
# seq(ymd(20211010),ymd(20211017), by=1)) #for sequence of days

not_here_dates <- c(
  # Fall Break
  seq(ymd(20221013),ymd(20221014), by=1),
  # ASC 2021
  seq(ymd(20221115),ymd(20221117), by=1),
  # Thanksgiving
  seq(ymd(20221123),ymd(20221127), by=1),
  # General Election Day
   ymd(20221108),
  # Southern ACJS
   seq(ymd(20220913),ymd(20220915), by=1)
  )

# You can adjust this as you see fit. Basically: add assignment types (e.g. papers, quizzes).
# My intro class was fairly simple: just exams.
#exam_dates <- c(ymd(20210218), ymd(20210401), ymd(20210429))

exam_dates <- seq(ymd(20221205), ymd(20221211), by=1)

# What are the full dates of the semester? Here, I'll exclude exam week as I like to do.
# In this case: 6 January to 23 April
semester_dates <- seq(ymd(20220818), ymd(20221211), by=1)

final_day <- mdy(12112022)

# Custom function for treating the first day of the month as the first week 
# of the month up until the first Sunday (unless Sunday was the start of the month)
wom <- function(date) {
    first <- wday(as.Date(paste(year(date),month(date),1,sep="-")))
    return((mday(date)+(first-2)) %/% 7+1)
  }

# Create a data frame of dates, assign to Cal
tibble(date = seq(ymd(20220801), ymd(20221231), by=1))  %>%
  mutate(mon = lubridate::month(date, label=T, abbr=F), # get month label
         wkdy = weekdays(date, abbreviate=T), # get weekday label
         wkdy = fct_relevel(wkdy, "Sun", "Mon", "Tue", "Wed", "Thu","Fri","Sat"), # make sure Sunday comes first
         semester = ifelse(date %in% semester_dates, 1, 0), # is date part of the semester?
         exams = ifelse(date %in% exam_dates, 1, 0), # is it an exam?
         not_here = ifelse(date %in% not_here_dates, 1, 0), # is it a day off?
         day = lubridate::mday(date), # get day of month to add later as a label
         # Below: our custom wom() function
         week = wom(date)) -> Cal

# Create a category variable, for filling.
# I can probably make this a case_when(), but this will work.

Cal %>%
  mutate(category = NA,
         category = ifelse(semester == 1, "Semester", category),
         category = ifelse(semester == 1 & wkdy %in% "Thu", "Class Day", category),
         category = ifelse(semester == 1 & wkdy %in% "Tue", "Class Day", category),
         category = ifelse(exams == 1, "Exams", category),
         category = ifelse(is.na(category) | (semester == 1 & not_here == 1), "NA", category)) -> Cal 

Cal %>% 
  ggplot(.,aes(wkdy, week)) +
  # custom theme stuff below
  # theme_steve_web() + 
  theme_bw() +
  theme(panel.grid.major.x = element_blank()) +
  # geom_tile and facet_wrap will do all the heavy lifting
  geom_tile(alpha=0.8, aes(fill=category), color="black", size=.45) +
  facet_wrap(~mon, scales="free", ncol=3) +
  # fill in tiles to make it look more "calendary" (sic)
  geom_text(aes(label=day),family="Open Sans") +
  # put your y-axis down, flip it, and reverse it
  scale_y_reverse(breaks=NULL) +
  # manually fill scale colors to something you like...
  scale_fill_manual(values=c("Class Day"="steelblue", 
                             "Semester"="lightsteelblue",
                             "NA" = "white", # I like these whited out...
                             "Exams"="indianred4"),
                    #... but also suppress a label for a non-class semester day
                    breaks=c("Class Day","Exams")) +
  labs(fill = "", x="", y="",
       caption = "Notable dates: Southern Criminology Conference (13-15 Sept), Fall Break (13-14 October), American Society of Criminology Conference (15-17 November), Thanksgiving Break (23-27 November)")  -> class_cal

```

```{r include = FALSE}

## Just need to change up the 'firstday` for most semesters.

library(tidyverse)
library(lubridate)
library(here)
library(kableExtra)

## for grading scheme

grades <- read_csv(here("CRJU 314", "grading-scheme.csv"))

## For discussion grading rubric
rubric <- read_csv(here("CRJU 314", "discussion-rubric.csv"))


firstday <- "2022-08-15"
    
meetings <- ymd(firstday) + c(0:16) * weeks(1)

meeting_headers <- paste0("Week ", 1:17, ", ", months(meetings), " ", day(meetings))

```

# Course Description

> "One of the beautiful things about science is that it allows us to bumble along, getting it wrong time after time, and feel perfectly fine as long as we learn something each time."

> Martin A. Schwartz (2008), ["The Importance of Stupidity in Scientific Research"](https://ir.stonybrook.edu/xmlui/bitstream/handle/11401/8083/schwartzimportanceofstupidityinscience.pdf?sequence=1)


Criminal law is a constant source of fascination. In addition to its prominent place on television networks’ schedules, criminal law governs the use of the most important form of governmental power: the power of government to incarcerate - and even execute. All forms of law govern human behavior, but criminal law governs the most basic questions of how we treat one another and defines those forms of human action which society will not tolerate. Criminal law also presents a number of questions central to political institutions, including the Executive and Judicial Branches, and the Bureaucracy.  This class is also intended as much as an examination these institutions and how they function within the context of criminal justice.  This class will not teach you the skills needed to serve as a criminal defense attorney (least of all, for yourself), but will engage you in a critical and engaged examination of our duties to others and the state’s role in regulating individuals’ actions.     

## Academic Bulletin

Origin and development of criminal law in America. Basic elements of crimes and defenses.

## Course Objectives

By the end of this course, students will be able to:

-  Identify the purpose, principles, and sources of US criminal law.
-  Distinguish between the major institutions of criminal law, and their role.
-  Describe the “legal equation” of major crimes, or the underlying elements.
-  Understand your role in the criminal justice system.
-  Critically assess criminal incidents
-  Effectively communicate regarding criminal justice incidents and concepts.

## Course Days, Times, Locations

**Section 001**: Tuesday/Thursday, 11:40a to 12:55p, Gambrel 151

**Section 002**: Tuesday/Thursday, 2:50p to 4:05p, WMBB Nursing 125

Gambrel Hall is [located at 817 Henderson Street](https://goo.gl/maps/dm4RBGwtwubSgmoN6).

WMBB is the Williams Brice Building, [located at 1601 Green Street](https://goo.gl/maps/asTDgUrXWdrPr91NA).

## Office Hours

What are [office hours](https://vimeo.com/270014784) anyway? I take a very liberal view of the word "office" and "hours." Most days, I'm literally sitting at a computer at home (or in a coffee shop on better days), webcam at the ready, and am happy to jump into a quick conversation with any student, at any time. We can meet individually or as a small group, speak by phone, or via a video call. If you want to make any type of appointment, please send me an email with a list of times you are available to meet.  You can either use the built-in Blackboard messaging system, or email directly at ian.adams@sc.edu.

# Required Materials

This class has a required electronic textbook. In addition, you will need to set up external accounts in order to complete reading assignments (called **"Smartbook Assignments"**) and discussion board assignments (called **"Packback Assignments"**). Both are covered below, and can be accessed directly from Blackboard by clicking on the appropriate assignment link. 


## Electronic Textbook

Garland (2022). Criminal Law for the Criminal Justice Professional, 5th Edition. McGraw-Hill, Incorporated. 

The Garland text above is required for a student to be successful in this course. You **must** have access to the electronic textbook, a hardcopy or previous edition will not be acceptable. The publisher has made an electronic version of the book available. If you have difficulty obtaining the textbook for any reason, please reach out to me as soon as possible. There may also be additional readings as distributed through Blackboard. 

### Required Textbook Readings: **Smartbook Assignments**

Chapter SmartBook activities are due on the stated due date listed in Blackboard. Clicking on the assignment will take you to the Connect external website, where you will complete the reading activity for each assigned chapter. These activities help students practice the concepts and objectives taught in the chapter readings and aid in preparing the student for the chapter assignments and exams.  You will continue to work through these activities until you have successfully completed each assignment.  Please note the amount of time to complete these activities varies by chapter.  If you have not read the chapter and become familiar with the content, these activities will take much more time than they are structured to take. 

## Required Discussion Technology - **Packback Assignments**

Participation is a requirement for this course, and the Packback Questions platform will be used for online discussion about class topics. Packback Questions is an online community where you can be fearlessly curious and ask open-ended questions to build on top of what we are covering in class and relate topics to real-world applications. 

### Packback Requirements

There will be a Weekly Monday at 11:59PM EST deadline for submissions. In order to receive full credit, you should submit the following per each deadline period:


-  Open-ended question every week with a minimum Curiosity Score of 50, worth 2pts of each assignment grade
-  Responses every week with a minimum Curiosity Score of 50, worth 4pts of each assignment grade
-  Half credit will be provided for questions and responses that do not meet the minimum curiosity score.

The minimum Curiosity score will increase throughout the semester!

### How to Register on Packback

Note: Only access Packback through Blackboard in order to ensure your grades sync properly.

-  Click the Packback assignment link within Blackboard to access the community
-  Follow the instructions on your screen to finish your registration.
-  In order for your grade to be visible in Blackboard, make sure to click each Packback assignment link as you post your Packback submissions.

Packback may require a paid subscription. Refer to www.packback.co/product/pricing for more information.

### How to Get Help from the Packback Team

If you have any questions or concerns about Packback throughout the semester, please read their FAQ at [help.packback.co](help.packback.co). If you need more help, contact their customer support team directly at help@packback.co. 

For a brief introduction to Packback Questions and why we are using it in class, watch this video: [https://www.youtube.com/watch?v=OV7QmikrD68](https://www.youtube.com/watch?v=OV7QmikrD68)




## Required Podcast

Listening to, considering, and responding to the issues posed in the *Serial* podcast are central tasks for this course. Feel free to use your preferred podcast platform. If you are having difficulty finding and listening to the podcast, please contact me immediately. Here are three examples of where to find the *Serial*, Season Three podcast episodes.

-  Podcast homepage: [Serial Podcast, Season 3](https://serialpodcast.org/season-three/1/a-bar-fight-walks-into-the-justice-center) 
-  Apple Podcasts: [Serial Podcast on Apple](https://podcasts.apple.com/us/podcast/serial/id917918570)
-  Stitcher Podcasts: [Serial Podcast on Stitcher](https://www.stitcher.com/podcast/this-american-life/serial)
-  Google Podcasts: [Stitcher Podcast on Google](https://podcasts.google.com/?feed=aHR0cDovL2ZlZWRzLnNlcmlhbHBvZGNhc3Qub3JnL3NlcmlhbHBvZGNhc3Q%3D)

## General Assignment Information

This class will require you to complete significant work. As an overview, you will be required to attend and participate in our class meetings; take quizzes; read assigned chapters from the textbook; listen to a podcast, and respond with a high-quality posting regarding that podcast episode(s); and there is a final exam. The bottom of this syllabus has more detailed information on assignment types and expectations.


## Finals Information

In this class you will have a final exam. This is worth substantial points and will heavily influence your final grade. The final exam will be taken in Blackboard (like your weekly quizzes), and is a mix of short answers and multiple choice questions of varying difficulty. As I'll say multiple times in this syllabus (and probably through the semester): There will be absolutely no class work of any kind (including the final) accepted after 11:59 p.m. on `r format(final_day, '%B %d, %Y')`.

# Contacting the Instructor

Normally, the fastest way to contact me is through the email above. I actively check and respond to emails throughout the day. I will always try to respond to your email within 72 business hours (i.e., Monday through Friday, exclusive of holidays). If you have a more urgent request, please note that within the subject line of your email.

Be sure to set your Blackboard settings such that you are notified when course messages are sent. All communications between students and instructors are to be respectful in content and professional in tone. Nonprofessional communications will be responded to with a request to rewrite/rephrase according to these communication expectations. In the case of emails and Blackboard messages, this means:

-  Using salutations (e.g., “Hello…”), closing statements (e.g., “Thank you for your attention to…”), and closings (e.g., “Best regards”). 
-  Stating the purpose of the email and including background information to enable the instructor to understand and respond to the email.
-  Using complete sentences and refraining from using profanity.

# Technology Requirements

All materials, links to articles, assignments, quizzes, and rubrics are located on the Blackboard site for the course. To participate in learning activities and complete assignments, you will need:

-  Access to a working computer that has a current operating system with updates installed, plus speakers or headphones to hear lecture presentations (transcripts provided);
-  Reliable Internet access and a USC email account;
-  A current Internet browser that is compatible with Blackboard (Google Chrome is the recommended browser for Blackboard); 
-  Microsoft Word as your word processing program; and
-  Reliable data storage for your work, such as a USB drive or Office365 OneDrive cloud storage.

If your computer does not have Microsoft Word, Office 365 ProPlus package is available to you free of charge and allows you to install Word, Excel, PowerPoint, Outlook, OneNote, Publisher, and Access on up to 5 PCs or Macs and Office apps on other mobile devices including tablets. Office 365 also includes unlimited cloud storage on OneDrive. To download Office 365 ProPlus, log into your student (University) email through a web browser, choose Settings (top right corner), and select software. If you have further questions or need help with the software, please contact the [Service Desk.](https://www.sc.edu/about/offices_and_divisions/university_technology_services/support/servicedesk.php)

## Blackboard Information

Minimum technical skills are needed in this course. All work in this course must be completed and submitted online through Blackboard. Therefore, you must have consistent and reliable access to a computer and the Internet. The minimum technical skills you have include the ability to:

-  Organize and save electronic files;
-  Use USC email and attached files;
-  Check email and Blackboard daily;
-  Download and upload documents;
-  Locate information with a browser; and
-  Use Blackboard.

## Technical Support

If you have problems with your computer, technology, IT-related questions, support, including Blackboard, please contact the Division of Information Technology (DoIT) Service Desk at (803) 777-1800 or submit an online request through the [Self-Service Portal](https://scprod.service-now.com/sp) or visit the [Carolina Tech Zone](https://sc.edu/about/offices_and_divisions/division_of_information_technology/end_user_services/available_technology_resources/carolina_tech_zone/). The Service Desk is open Monday – Friday from 8:00 AM – 6:00 PM (Eastern Time). If you are located in the Columbia, SC area, the Thomas Cooper Library at UofSC has computers for you to use in case you encounter computer issues/problems. If you are not located in the Columbia, SC area, most regional campuses and public libraries have computers for public use.

# Class Schedule

Students must read all assigned material prior to our class session.  Important: class readings are subject to change, contingent on mitigating circumstances and the progress we make as a class.  Students are encouraged to attend lectures and check the course Blackboard website for updates. 

Here is an overview calendar for the course. The semester is in light blue, meeting days are highlighted in darker blue. Final exam week is highlighted in red. If a date is white, that means no class due to breaks. 

```{r calendar, echo=F, eval=T, fig.cap="Calendar for PoLS 3220: Jurisprudence of Criminal Law, Fall 2021",  warning=F, fig.width=11, fig.height=7}

class_cal

```



This course is arranged into topics for each week, which correspond with our textbook chapters. Please see the Blackboard course for details and links for each week's activities. Note that the dates below mark the *start of the week,* not the date of our class meetings, which are Tuesdays and Thursdays. Also note that in weeks with a holiday that covers one of our classes for the week, we will still plan on meeting for the other day. **You are expected to still complete the week's reading and assignments even if we are not meeting on both class days!**

##  `r meeting_headers[1]` : 

**Topics:** Class Introduction; Nature, Purpose, and Function of Criminal Law

**Readings:** Syllabus, Code of Conduct, Chapter 1


##  `r meeting_headers[2]` : 

**Topics:** Constitutional Limitations

**Readings:** Chapter 2


##  `r meeting_headers[3]` :

**Topics:** Classifications of Crime

**Readings:** Chapter 3


##  `r meeting_headers[4]` : 

**Topics:** Parties to Crime

**Readings:** Chapter 4

##  `r meeting_headers[5]` :

*No class this week (Southern Criminology Conference) - you must still complete all assignments in Blackboard! See you next week!*

**Topics:** Incomplete Crimes

**Readings:** Chapter 5


##  `r meeting_headers[6]` :

**Topics:** Defenses to Crime

**Readings:** Chapter 6


##  `r meeting_headers[7]` :

**Topics:** Punishment & Sentencing

**Readings:** Chapter 7


##  `r meeting_headers[8]` :

**Topics:** Criminal Homicide

**Readings:** Chapter 8


##  `r meeting_headers[9]` :

*No class on Oct. 13 (Thursday) - Fall Break!*

**Topics:** Crimes Against Persons: Other Offenses

**Readings:** Chapter 9


##  `r meeting_headers[10]` :

**Topics:** Crimes Against Habitation

**Readings:** Chapter 10

##  `r meeting_headers[11]` :

**Topics:** Crimes Against Property

**Readings:** Chapter 11

##  `r meeting_headers[12]` :

**Topics:** White Collar Crimes

**Readings:** Chapter 12


##  `r meeting_headers[13]` :


**Topics:** Crimes Against Public Order, Safety, and Morality

**Readings:** Chapter 13

##  `r meeting_headers[14]` :

*No class meetings this week as I will be attending the 2022 American Society of Criminology Conference. You are still expected to complete the readings and the quiz!*

**Topics:** Drug and Alcohol Related Crimes

**Readings:** Chapter 14

##  `r meeting_headers[15]` :

*No class on Nov. 24 (Thursday) for Thanksgiving. Enjoy your holiday, and see you next week!*

**Topics:** Crimes Against the Administration of Justice

**Readings:** Chapter 15

##  `r meeting_headers[16]` :

**Topics:** Organized Crime, Gangs, & Terrorism

**Readings:** Chapter 16

##  `r meeting_headers[17]` :

**FINALS WEEK & FINAL EXAM** Your final exam is due **no later than 11:59 p.m. on `r format(final_day, '%B %d, %Y')`**. There will *absolutely* be no assignments, quizzes, or exams accepted after that date and time. None. Add it to your calendar now. Failure to submit any assignment, quiz, or exam by that date and time will automatically be counted as a zero towards your final grade. I will accept no appeals on this, so please plan ahead.

**Final Exam:** Final Exam is available during finals week (`r format(exam_dates, '%B %d, %Y')`), and is due by 11:59 p.m. on **`r format(final_day, '%B %d, %Y')`**. This means you have approximately one week in which to complete the exam.


# Course Policies

I will detail the various policies for this course below. These are very important to your success in this class, and you should be familiar with them!

## Academic Honesty

Academic honesty is expected, and dishonesty will not be tolerated. The University policy on academic dishonesty can be found on the university website. An act of academic dishonesty will result in a failing course grade and a recommendation of additional disciplinary action. The faculty has adopted guidelines concerning what constitutes a violation of ethical standards for work completed in this course. Any of these violations will be considered academic dishonesty and treated as such. These guidelines are in addition to any University-wide guidelines concerning academic dishonesty, which may be in effect. All course assignments will be scanned for plagiarism, and any misconduct will result in a failing grade for the course. 

1.	__Cheating__: the giving or receiving of any unauthorized assistance on any academic work;
2.	__Plagiarism__: presenting the language, structures or ideas of another person or persons as one’s own academic work;
3.	__Falsification__: Any untrue statement, either oral or written, concerning one’s own academic work or the academic work of another student, or the unauthorized alteration of any academic record; and
4.	__Original work & "Self Plagiarism"__: Unless specifically allowed by the instructor, all academic work undertaken in a course must be original (i.e., it must not have been submitted in a prior course or be submitted in a course being taken concurrently).

## Respectful & Appropriate Class Conduct

Public policy processes, including the criminal justice system, inherently center on topics and issues for which individuals hold strong opinions, based on their personal values, beliefs, and interests. As a result, this course will challenge students to not only acknowledge and respect perspectives that differ from their own, but may call on them to challenge their own opinions and beliefs, and “step into” another’s perspective to consider the strengths and limitations of their own argument. 

In order to facilitate this process and ensure a socially, emotionally, and psychologically safe environment, **respectful behavior is the expectation, norm, and requirement in this class.** Arguments and ideas may (and are expected to) be challenged, but personal attacks, disrespectful behavior, and/or hateful attitudes towards people or any groups of people will not be tolerated.

## Course Work

This class will require you to complete significant work outside of class. As an overview, you will be required to attend and participate in class meetings; take quizzes; read assigned chapters from the textbook; listen to a podcast, and respond with a high-quality posting regarding that podcast episode(s); complete one essay; and there is a final exam.

### Grading and Points Distribution

This class has *approximately* 579 points available through quizzes, assignments, and discussions:

- Orientation quiz - 6 points - About **1%** of your grade
- Weekly quizzes - 225 points - About **39%** of your grade
- Packback discussions - 78 points - About **13%** of your grade
- Smartbook readings - 150 points - About **26%** of your grade
- Final Exam - 120 points - About **21%** of your grade

Please keep in mind that these are approximations. Throughout the course I may modify the course and assignments as needed. 

### Weekly Quizzes

Each week you are required to answer a short quiz. The questions in every quiz are drawn directly from that week’s lecture and readings. The questions are also very similar to the questions you will encounter in the final exam! If you are keeping up on your reading, they should not pose too much difficulty. The questions are randomly drawn from a large pool of questions, so each student will be presented with a different quiz. 

### Discussion Postings

Every week, I will post a starter question on a discussion thread in Packback. In the first half of the course, these postings relate to episodes in a podcast: “Serial: Season 3,” which describes the criminal justice system in Cleveland, Ohio. The second half of the course will have discussions regarding a criminal justice issue in the news. 

Some advice and rules: 

(a)	Do not wait until the last day to make your postings. This requirement will ensure that you have plenty of response options over the weekend when it comes to posting a response. *Post early, post often*.

(b)	When you post something on the discussion board, you should try to use class material, current events, and inject your personal opinion backed by evidence. A high-quality mandatory posting will be at least two paragraphs in length (but need not necessarily be more than two paragraphs) and will contain a cogent argument which responds directly to the question asked and does not contain spelling or grammatical errors. A high-quality posting in response to another students posting may be slightly shorter in length than the initial posting (but should be at least one full paragraph in length, or 4-5 sentences) and should still contain a cogent argument and correct spelling and grammar.

(c)	Each of the posting assignments is worth up to 6 points – in other words, you could receive less than 6 points if your posting does not conform to the course criteria. 

(d)	Although I want to use this portion of the class to foster a healthy and vigorous debate between students, I reserve the right to delete any posting I choose. I will delete a posting if it is unreasonably derogatory towards another student or violates university policy. Otherwise, the posting board will be fair game. If I delete your posting, you will not receive credit for it. In short, engage with each other, but please make every effort to be respectful.


```{r remedy002, eval=FALSE, include=FALSE}

# kbl(rubric,
#     format = "latex",
#     booktabs = TRUE,
#     caption = "Discussion Grading Rubric") #%>%
  #kable_styling(latex_options = "scale_down")

```

### Late Policy

All quizzes submitted after the due date are subject to a **ten percent deduction**. An additional ten percent is deducted for each additional 24 hours the assignment is late. Please note the specific due dates for all assignments. **No deadlines past `r format(final_day, '%B %d, %Y')` will be considered or accepted**. Missing submissions will be awarded zero points automatically. Perhaps the the most important point -- contact me beforehand if you are experiencing difficulties that will impact your ability to turn in work! Reaching out after the due date has passed is not helpful to you or me.

## Grading Scheme 

The course grading scheme is as follows. When a course grade falls between integers, I apply a standard rounding procedure: any point total that ends in .0 to .49 will be rounded down to the nearest whole number, while any point total that ends in .50 to .99 will be rounded up. Note that this is done automatically by Blackboard. I do not grade on a curve, and would be delighted to be able to give every student an A. However, it is up to you to be consistent, motivated, and engaged. 

```{r remedy003, echo=FALSE}

kbl(grades, "latex")

```


### Contested Grades

If you would like your discussion or quiz regraded, please email me in advance of our meeting. In this email, please state clearly what the issue is and the reasons that you feel justify an adjustment to your grade. Once I receive your email, we will schedule an in-person meeting to discuss your request. Please be aware, if I agree to regrade, the entire assignment will be evaluated again. This means that your grade can be lowered as well as raised. The new grade will be final. 

If you just have questions on a quiz question, there is no need to request a full regrade. Simply email me and we will discuss, or bring it up in class. Note that no regrading will be done for the final exam and essay, as the semester will have ended.

## Attendance Policy

```{r, include=FALSE}
# I like to put in a cautionary tale about the importance of attending classes. This will approximate the underlying data.
# Data are clearly fake, though.

tibble(perattend = rbnorm(800, 81.84, 22.74, 0, 100),
       grade = 10.19 + .78*perattend + rnorm(800, 0, 20),
       rgrade = case_when(
         grade < 0 ~ 0,
         grade > 100 ~ 100,
         TRUE ~ grade
       )) -> Attend

options(scipen=999)
M1 <- lm(rgrade ~ perattend, Attend)
M2 <- lm(rgrade ~ perattend, data=subset(Attend, perattend >= 75))

M1df <- broom::tidy(M1)
M2df <- broom::tidy(M2)
#library(ggplot2)
#library(kfigr)
```

Attendance is mandatory for our weekly class meetings. We all have busy lives, so being late is not a problem (though not preferred), and I’d rather you miss ten minutes than a whole class. Students are expected to fully engage in the discussion in each class. *The purpose of the class is for everyone to discuss the readings, not to have them explained.* I will not take formal attendance if the class is small; however, in larger classes, attendance may be marked. In either case, failure to regularly attend and participate in class discussion will negatively affect your grade. Consider the following, courtesy [Steven Miller](https://github.com/svmiller).

A simple linear regression of a student's final grade on percentage of classes attended for the semester suggests an increase of one percent in attendance for the semester leads to an estimated increase of `r round(M1$coefficients[2], 3)` in the student's final grade. Whereas one missed classes constitutes about a five-percent decrease in percentage attendance for the semester, one missed class means an estimated decrease of `r round(M1$coefficients[2], 3)*5` in the overall grade. The effect of attendance on the final grade for the class is precise (*t* = `r round(M1df$statistic[2], 3)`) and the likelihood that there is no actual relationship between attendance and final grade for the semester is almost zero. This simple linear model with just one predictor (attendance) provides a good fit as well (R$^2$ = `r round(summary(M1)$r.squared, 3)`). See Figure 2 in this document.

```{r attendplot, echo = FALSE, results="asis", cache=FALSE, fig.cap="A Scatterplot of the Relationship between Class Attendance and Final Grade", fig.height=4, fig.pos="H"}
Graph <- ggplot(Attend, aes(x = perattend, y = rgrade))
Graph + geom_point() + labs(x="Percent Attendance in Class", y="Final Grade in Class (0-100)") + 
                              geom_smooth(method=lm)
```

The findings hold even when I subset the data to cases where attendance is greater than 75% (i.e. roughly the threshold below which I deduct all participation points). Students who just meet the threshold for full participation points nevertheless get an estimated decrease of `r round(M2$coefficients[2], 3)*5` in their overall grade for each missed class. This effect is also precise (*t* = `r round(M2df$statistic[2], 3)`). Put another way, we would have observed this effect in my data if there were no *true* effect of attendance on grades about `r round(summary(M2)$coefficients[2,4]*100000)` times in 100,000 "trials" (i.e. *p* = `r round(summary(M2)$coefficients[2,4], 5)`), on average. That probability is effectively zero. *Attend class*.

## Instructor Expectations

I commit to being your mentor and facilitator of the classroom experience, and to the following expectations for this course:

- I will design the course to include lectures, readings materials, and assignments that will challenge students and will provide them with opportunities to learn and practice course content.
- Though this course has online components (quizzes, discussions, etc.), it is not a class that is run “automatically” by technology. I interact with the class via announcements, virtual office hours, emails/the Blackboard Inbox, feedback on assignments, discussion and lecture in class, and comments on lecture bulletin boards, among other methods.
- I will respond to emails in a timely fashion. “Timely” in this instance means within 24-72 hours, not including weekends and holidays. *Normally*, I am quite a bit faster, but like everyone else, life sometimes intervenes. If you do not hear from me within 72 hours, please email again.
- I will be available for individual consultation via virtual office hours, email, or phone. Students will not be required to come to campus in order to meet with me, nor does it have to be during 'bankers hours.'
- I will provide feedback on assignments in a timely manner.
- I will ensure and enforce a respectful atmosphere.
- I will maintain a classroom that is open to questions, discussion, and ethical disagreement.
- I will follow all [official University of South Carolina policies](https://academicbulletins.sc.edu/undergraduate/policies-regulations/undergraduate-academic-regulations/#text) regarding conduct in the classroom, incompletes, and accommodations. Accommodations will be considered on an individual basis and only with required documentation. See the **University Policies** section at the end of this syllabus for more information and resources.

## Student Expectations

Though there is some built in flexibility, in that you are able to complete quizzes within a module rather than a specific date, can turn in the final essay before finals week, and have about a week in which to complete the final exam, this course does have a structure and timeline, including due dates for course assignments. As such, the following is expected of all students in this class:

- Students will log in to the course each week.
- Students will attend class meetings each week.
- Students may be expected to work with classmates; however, students are not expected to necessarily interact with their classmates in person. A good alternative to meeting in person would be online video conferencing, which allows students to find a time to meet that works best for their schedule. Depending on the assignment, students can also choose to interact with their classmates with whatever technology they are most comfortable with.
- To do well, students must be self-motivated, organized, and willing to stay on top of their schedule. Students should take control of their learning while in this course.
- Students will regularly check course announcements. The *Announcements* area is the instructor’s official means of communication when distributing information to the entire class.
- Students will update their Blackboard settings to ensure they receive timely notifications from the course.
- If students have any questions, are struggling with course materials, or need further assistance from their instructor, they will take the initiative to contact their instructor via the Inbox feature in Blackboard or via email. Email is not perfect; sometimes, messages sent to instructors are lost before they are read. If you do not hear back from your instructor within 72 hours after sending a message, please contact me again.
- Students will engage with the course, students, and the instructor in a respectful and professional manner at all times.

## Copyright/Fair Use

I will cite and/or reference any materials that I use in this course that I do not create.  You, as students, are expected to not distribute any of these materials, resources, quizzes, tests, homework assignments, etc. (whether graded or ungraded).


# University Policies

It is my intent that students from all diverse backgrounds and perspectives be well served by this course, that students’ learning needs be addressed both in and out of class, and that the diversity that students bring to this class be viewed as a resource, strength, and benefit. It is my intent to present materials and activities that are respectful of diversity: gender, sexuality, disability, age, socioeconomic status, ethnicity, race, and culture. Your suggestions are encouraged and appreciated. Please let me know ways to improve the effectiveness of the course for you personally or for other students or student groups. In addition, if any of our class meetings conflict with your religious events, please let me know so that we can make arrangements for you. The following resources and statements are drawn directly from the University of South Carolina policies, values, and mission. If you have questions or concerns not answered below, please contact me directly so we can work together to answer and address them.

*Accommodation of Sincerely Held Beliefs*:  I will work with students who require schedule changes due to religious or other significant obligations. I will not consider any requests based on course content. No other area of study touches on more sensitive topics than the broad category of "public policy" (and at times disturbing forms of human misbehavior such as criminal law). Policy researchers must read about, talk about, and listen to information relating to very difficult subjects. Sometimes case descriptions can be quite graphic. Students are required to attend all classes and to read all the assignments. All assignments and lectures are related to our subject matter.

*Veterans and Military Services*. If you are a student veteran or military services member, the University of South Carolina  has a Veterans and Military Services Center, located at 901 Sumter Street, Suite 105. Hours: M-F 0830a-1700 hours. Please visit their website for more information about what support they offer, a list of ongoing events, and links to outside resources: [Veterans and Military Services](https://sc.edu/about/offices_and_divisions/veterans_and_military_services/index.php). Please also let me know if you need any additional support in this class for any reason.

*Diversity and Inclusion*:  The university is committed to a campus environment that is inclusive, safe, and respectful for all persons, and one that fully embraces the Carolinian Creed. To that end, all course activities will be conducted in an atmosphere of friendly participation and interaction among colleagues, recognizing and appreciating the unique experiences, background, and point of view each student brings. You are expected at all times to apply the highest academic standards to this course and to treat others with dignity and respect.
	
*Accessibility, Disability, and Triggers*:  I am committed to ensuring course accessibility for all students. If you have a documented disability and expect reasonable accommodation to complete course requirements, please notify me at least one week before accommodation is needed. Please also provide [SDRC](https://sc.edu/about/offices_and_divisions/student_disability_resource_center/) documentation to me before requesting accommodation. Likewise, if you are aware of cognitive or emotional triggers that could disrupt your intellectual or mental health, please let me know so that I can be aware in terms of course content.

*Diversity, Ethics, and the Carolinian Creed*:  This course works to foster a climate free of harassment and discrimination, and it values the contributions of all forms of diversity. The decision to enter university and pursue advanced study is a choice that entails commitment to personal ethics expressed in the [Carolinian Creed](www.sa.sc.edu/creed): “I will discourage bigotry, while striving to learn from differences in people, ideas and opinions.” Likewise, the [Student Code of Conduct STAF 6.26](http://www.sc.edu/policies/ppm/staf626.pdf) stresses, “The University of South Carolina strives to maintain an educational community that fosters the development of students who are ethical, civil and responsible persons.”

*Title IX and Gendered Pronouns*:  This course affirms equality and respect for all gendered identities and expressions. Please don’t hesitate to correct me regarding your preferred gender pronoun and/or name if different from what is indicated on the official class roster. Likewise, I am committed to nurturing an environment free from discrimination and harassment. Consistent with Title IX policy, please be aware that I as a responsible employee am obligated to report information that you provide to me about a situation involving sexual harassment or assault. 

*Values [credit to Dr. David Moscowitz]*:  Two core values, inquiry and civility, govern our class. Inquiry demands that we all cultivate an open forum for exchange and substantiation of ideas. Strive to be creative, to take risks, and to challenge our conventional wisdom when you see the opportunity. Civility supports our inquiry by demanding ultimate respect for the voice, rights, and safety of others. Threatening or disruptive conduct may result in course and/or university dismissal. Civility also presumes basic courtesy: please be well rested, on time, and prepared for class, and silencing all personal electronic devices. My perspective is that we never cease being students of this world, so I believe that attentive, reflective people always have something to learn from others. Good discussions can be energetic and passionate but are neither abusive nor offensive. Vibrant, vigorous inquiry derives from discussions that:

-  challenge, defend, and apply different ideas, theories, perspectives, and skills, 
-  extend a body of knowledge into different arenas and applications, and 
-  result in a synergy that compels us to seek resolution to these discussions.

# Academic Success

(@) Disability Services

[Student Disability Resource Center](http://www.sa.sc.edu/sds/): The Student Disability Resource Center (SDRC) empowers students to manage challenges and limitations imposed by disabilities. Students with disabilities are encouraged to contact me to discuss the logistics of any accommodations needed to fulfill course requirements (within the first week of the semester). In order to receive reasonable accommodations from me, you must be registered with the Student Disability Resource Center (1705 College Street, Close-Hipp Suite 102, Columbia, SC 29208, 803-777-6142). Any student with a documented disability should contact the SDRC to make arrangements for appropriate accommodations.

(@) Student Success Center

In partnership with UofSC faculty, the Student Success Center (SSC) offers a number of programs to assist you in better understanding your course material and to aid you on your path to success. SSC programs are facilitated by professional staff, graduate students, and trained undergraduate peer leaders who have previously excelled in their courses. Resources available to you in this course may include:

-  Peer Tutoring: You can make a one-on-one appointment with a [Peer Tutor](www.sc.edu/success).  Drop-in Tutoring and Online Tutoring may also be available for this course. Visit their website for a full schedule of times, locations, and courses.
-  Supplemental Instruction (SI): SI Leaders are assigned to specific sections of courses and hold three weekly study sessions. Sessions focus on the most difficult content being covered in class. The SI Session schedule is posted through the SSC website each week and will also be communicated in class by the SI Leader.
-  Peer Writing: Improve your college-level writing skills by bringing writing assignments from any of your classes to a Peer Writing Tutor. Similar to Tutoring, you can visit the website to make an appointment, and to view the full schedule of available drop-in hours and locations.
-  Success Consultations: In Success Consultations, SSC staff assist you in developing study skills, setting goals, and connecting to a variety of campus resources. Throughout the semester, I may communicate with the Student Success Center regarding your progress throughout the semester, which indicates your instructor is concerned about your progress in this course. If contacted by the Student Success Center, please schedule a Success Consultation right away. Referrals are not punitive, and any information shared by your professor is confidential and subject to FERPA. Student Success Center services are offered to all UofSC undergraduates at no additional cost. Please call 803-777-1000, visit [www.sc.edu/success](www.sc.edu/success), or come to the Student Success Center in the Thomas Cooper Library (Mezzanine Level) to check schedules and make appointments.

SSC services are offered to all UofSC undergraduates at no additional cost. You are invited to call the Student Success Hotline at (803) 777-1000, [visit the SSC website](www.sc.edu/success), or stop by the SSC in the Thomas Cooper Library on the Mezzanine Level to check schedules and make appointments. 

(@) Writing Center

[Writing Center](http://artsandsciences.sc.edu/write/university-writing-center)
This course has many of writing assignments. The University Writing Center is an important resource you should use! It's open to help any UofSC student needing assistance with a writing project at any stage of development. The main Writing Center is in Byrnes 703.

(@) University Library Resources

[University Libraries Resources](sc.edu/libraries)

-  University Libraries has access to books, articles, subject specific resources, citation help, and more. If you are not sure where to start, please Ask a Librarian!  Assistance is available at [sc.edu/libraries/ask](sc.edu/libraries/ask).  
-   Remember that if you use anything that is not your own writing or media (quotes from books, articles, interviews, websites, movies – everything) you must cite the source in MLA, APA, or Chicago citation styles (or other appropriate and approved) format.

(@) Blackboard and Technology

[Blackboard and Technology](https://sc.edu/about/offices_and_divisions/division_of_information_technology/end_user_services/available_technology_resources/)
As a student in this course, you have access to support from the Division of Information Technology (DoIT) for Blackboard and computer issues. The service desk can be reached at 803-777-1800.

(@) Counseling Services

[Counseling Services](https://sc.edu/about/offices_and_divisions/student_health_services/medical-services/counseling-and-psychiatry/index.php): The University offers counseling and crisis services as well as outreach services, self-help, and frequently asked questions.

(@) Mental Health

If stress is impacting you or getting in the way of your ability to do your schoolwork, maintain relationships, eat, sleep, or enjoy yourself, please reach out to any of our mental health resources. Counseling & Psychiatry offers individual and group counseling and psychiatric services. You can schedule an appointment at (803) 777-5223 or on MyHealthSpace. You can also call after-hours for crisis counseling. Wellness Coaching can help you improve in areas related to emotional and physical wellbeing, such as sleep, resiliency, balanced eating and more. Wellness Coaching appointments can be made by calling 803-777-6518 or on MyHealthSpace. You can also access virtual self-help modules via [Therapy Assistance Online (TAO)](https://us.taoconnect.org/register). Most of these services are offered at no cost as they are covered by the University Health Services tuition fee. For all available mental health resources, check out [University Health Services Mental Health](https://sc.edu/about/offices_and_divisions/health_services/mental-health/index.php).

(@) Interpersonal Violence

Interpersonal violence - including sexual harassment, relationship violence, sexual assault, and stalking - is prohibited at UofSC. Faculty, staff, and administrators encourage anyone experiencing interpersonal violence to speak with someone, so they can get the necessary support and UofSC can respond appropriately. If you or someone you know has been or is currently impacted by interpersonal violence, you can find the appropriate resources at the [Stop Interpersonal Violence](http://www.sc.edu/stopsexualassault) website. 

As faculty, I must report all incidents of interpersonal violence and sexual misconduct, and thus cannot guarantee confidentiality. Please know that you can [seek confidential resources](https://sc.edu/about/initiatives/safety/stop_sexual_assault/contacts/index.php). If you want to make a formal report, [you can report here](https://cm.maxient.com/reportingform.php?UnivofSouthCarolinaEOP&layout_id=6) or contact the institution’s Title IX Coordinator, or one of the Deputy Title IX Coordinators listed on the Stop Sexual Assault website. You can also file a police report by contacting USC Police at 803-777-4215. 















